Analyzing the Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-03 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

Home-court advantage is the basic idea that the home team is more likely to win.
So laying a foundation of typical home-court advantage is crucial. Before 
focusing on the 2017 to 2020 playoffs we can take a quick look at home team win
percentages since 2010. Notice in Figure \@ref(fig:Fig1), the10 years before 2020, the home team
winning percentage ranged from around 0.56 to 0.7 and never dipped below .5. The 
2020 bubble, however, broke this historicpattern dipping down below .5. Foreshadowing, 
the confirmation of the expectationthat the effect of home-court advantage was removed
in the 2020 playoffs.

@@

Figure \@ref(fig:Fig3) shows home shooting for two pointers, three pointers and
free throws for 2020(top) vs. 2017-19(bottom). The histograms appear to be fairly
similarly distributed between 2020 and 2017-19. Likewise, Figure \@ref(fig:Fig4),
shows the same data except for away teams. Just like Figure \@ref(fig:Fig3),
Figure \@ref(fig:Fig4) histograms don’t show anyobvious differences. The normality
of the distributions in both Figure \@ref(fig:Fig3) and Figure \@ref(fig:Fig4) are
important for meeting the required assumptions for statistical analysis.

>>>>

Home-court advantage is the basic idea that the home team is more likely to win.
So laying a foundation of typical home-court advantage is crucial. Before 
focusing on the 2017 to 2020 playoffs we can take a quick look at home team win
percentages since 2010. Notice in Figure \@ref(fig:Fig1), the 10 years before 2020, the home team
winning percentage ranged from around 0.56 to 0.7 and never dipped below .5. The 
2020 bubble broke this historic pattern dipping down below .5. Foreshadowing, 
the confirmation of the expectation that the effect of home-court advantage was removed
in the 2020 playoffs.

@@

Figure \@ref(fig:Fig3) shows home shooting for two pointers, three pointers and
free throws for 2020(top) vs. 2017-19(bottom). The histograms appear to be fairly
similarly distributed between 2020 and 2017-19. Likewise, Figure \@ref(fig:Fig4),
shows the same data except for away teams. Just like Figure \@ref(fig:Fig3),
Figure \@ref(fig:Fig4) histograms don’t show any obvious differences. The normality
of the distributions in both Figure \@ref(fig:Fig3) and Figure \@ref(fig:Fig4) are
important for meeting the required assumptions for statistical analysis.
